Chinese Poem Generator from Image

### 2015-12-01 paper.tex
modify

\author{Kelei Cao\\
Tsinghua University \\
Computer Science \& Technology\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Dichen Qian\\
Tsinghua University \\
Computer Science \& Technology\\
{\tt\small nathenqian@gmail.com}
}

@@

\subsection{Plan}
\subsubsection{Image to Sentence}
The first part of this problem is to generate a sentence based on the image. This sentence must contain the detail of this image, and it can describe this image.
\subsubsection{English to Chinese}
The sentence is English, so we need to change it from English to Chinese so that we can process our next step.
\subsubsection{Sentence to Poem}
The second part of this problem is to generate the poem base on the sentence. What need to do is extracting the feature from the sentence and use them to generate the poem.

\section{Related Work}

%-------------------------------------------------------------------------

\end{document}

>>>>

\author{Kelei Cao\\
Tsinghua University \\
Computer Science \& Technology\\
{\tt\small ckl13@mails.tsinghua.edu.cn}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Dichen Qian\\
Tsinghua University \\
Computer Science \& Technology\\
{\tt\small nathenqian@gmail.com}
}

@@

\section{Related Work}
	Generating poem is popular in recent years, and there are many people research on it. On the other hand, explain image with sentence has also made great progress after deep learning widely used. Our approach is a combination of above two aspects, we select two methods that performing well in corresponding aspects, and try to get a fantastic result.
\section{Plan}
\subsection{Image to Sentence}
The first part of this problem is to generate a sentence based on the image. This sentence must contain the detail of this image, and it can describe this image.

The method we want to use here is proposed by Junhua Mao\footnote{ Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L. Yuille : Explain Images with Multimodal Recurrent Neural Networks.}. We use a multimodal Recurrent Neural Networks (m-RNN) model to address both the task of generating novel sentences descriptions for images, and the task of image and sentence retrieval. The whole m-RNN architecture contains a language model part, an image part and a multimodal part. The language model part learns the dense feature embedding for each word in the dictionary and stores the semantic temporal context in recurrent layers. The image part contains a deep Convulutional Neural Network (CNN) \footnote{A. Krizhevsky, I. Sutskever, and G. E. Hinton. Imagenet classification with deep convolutional neural networks. In NIPS, pages 1097–1105, 2012.} which extracts image features.

\subsection{Translate and Extract}
Now we get the sentence, as to generate the meaningful poetry, we need to extract keywords from the sentences. We can use a translation process to deal the sentence and only use the words that appears in Chinese poetry dataset that we used in poem generator.

\subsubsection{Poem generator}
	The method we will use to generate poem is proposed by Mirella Lapata\footnote{Xingxing Zhang, Mirella Lapata : Chinese Poetry Generation with Recurrent Neural Networks.}.First, to create the first line of poem, We select all phrases corresponding to the users’s keywords and generate all possible combinations satisfying the tonal pattern constraints. We use a language model to rank the generated candidates and select the best ranked one as the first line in the poem. In implementation, we employ a character-based recurrent neural network language model.
	And after that, we generate the rest poem lines with original lines. Convert lines $s_1$...$s_i$ into vectors $v_1$...$v_i$ with a convolutional sentence model (CSM). Next, a recurrent context model (RCM) takes $v_1$...$v_i$ as input and outputs $u_{j,i}$.Finally, $u_{1,i}$, $u_{2,i}$,...,$u_{j,i}$ and the first $j$ characters $w_1$...$w_j$ in line $s_{i+1}$ serve as input to a recurrent generation model (RGM) which estimates $P(w_{j+1} = k | w_{1:j} ,s_{1:i} )$ with $k\in V$, the probability distribution of the $j+1$ th character over all words in the vocabulary $V$.
%-------------------------------------------------------------------------
\section{Dataset}
The dataset we used is IAPR TC-12 dataset, which used to training the model that explain image. The other is Chinese Poetry corpus.
\section{Intermediate Result}
We have built a temporary framework and consulted one expert about this problem. The expert thought it's a very good idea and gave some advices.
We will soon try to use theano to implement our idea, for this week is the deadline of building a cpu.
\end{document}
